fromFobLisa, Version 2

### 2018-03-04 CreData/fromFobLisa.Rmd
last minute

```{r lisadat}
load("../../Data/lisa.rda")
lisa <- lisa[lisa$KOMMUN %in% ourkom, ]
indx <- match(lisa$LINNEID, per$LINNEID)
lisa$birthdate <- per$birthdate[indx]
```

Those with *missing birthdate* in *lisa* are those born 1975 or later (What??). They can be removed.

```{r removeyoung}
lisa <- lisa[!is.na(lisa$birthdate), ]
```

@@

```{r cleanandsort}
##lisadata <- age.window(lisa, c(40, 110))
lisadata <- lisa[order(lisa$LINNEID, lisa$enter), ]
lisadata <- cal.window(lisadata, c(1987, 2014)) # 'Remove lisa2013'
rownames(lisadata) <- 1:NROW(lisadata)
save(lisadata, file = "lisadata2.rda")
```

@@

Note, this is just cut from "Mort2/CreateData2/fromFobLisa.Rmd". May need
some editing ...

```{r gethislisa}
    load("../../Data/socstyr.rda")
    indx <- match(fobdata$LINNEID, socstyr$LINNEID)
    fobdata$ULORSAK <- str_trim(as.character(socstyr$ULORSAK[indx]))
    source("R/putONssyk.R")
    ##putONssyk
    fobb <- putONssyk(fobdata)
    source("R/ssykTOhisclass.R")
    ##ssykTOhisclass
    fobb$hisclass <- ssykTOhisclass(fobb$ssyk)
    is.na(fobb$hisclass) <- with(fobb, is.na(hisclass) |
                                       (!is.na(hisclass) & hisclass == -1))
    source("R/addPer.R")
    ##fobb <- pushHis(fobb)
    ##fobb$hisclass <- fobb$nyhisclass
    ## Instead
    ##fobb <- group_by(fobb, LINNEID) %>% fill_("hisclass") # Later!
    fobb$id <- fobb$LINNEID
    fobb <- addPer(fobb, cuts = c(1961, 1971, 1981, 1991, 2002))
    load("../../Data/sex.rda")

    indx <- match(fobb$LINNEID, sex$LINNEID)
    fobb$KON <- sex$KON[indx]
    fobb$urban <- fobb$FORSAMLING %in% c(248001, 248002, 284004, 284005,
                                         248011, 248201, 248204)
    civst <- numeric(NROW(fobb))
    civst[fobb$CIVIL %in% c(0, 5)] <- 1 # Ogift
    civst[fobb$CIVIL %in% c(2, 7)] <- 2 # Gift, sambo
    civst[fobb$CIVIL %in% c(1, 3, 4, 6, 8, 9)] <- 3 # skild, änka
    fobb$civst <- factor(civst,
                         labels = c("unmarried", "married", "prev.married"))
    fobb$sex <- fobb$KON
    levels(fobb$sex) <- c("male", "female")
    fobb <- fobb[, c("id", "AR", "birthdate", "sex", "enter", "exit", "event",
                     "period", "urban", "civst", "hisclass", "ULORSAK")]
   fobb$dataset <- as.character(fobb$AR)
```

## Lisa

@@

    ## Fix HISCLASS:
    source("R/ssyk3TOhisclass.R")
    ##ssyk3TOhisclass
    lisadata$hisclass <- ssyk3TOhisclass(lisadata$SSYK3)
    ## Push forward:
    source("R/pushHis.R")
    ## liss <- pushHis(lisadata) # Later!
    liss <- lisadata
    ##liss$hisclass <- liss$nyhisclass
    ##liss$nyhisclass <- NULL
    ## Now:
    ##liss <- group_by(lisadata, LINNEID) %>% fill_("hisclass") # Later!!
    liss$id <- liss$LINNEID
    lisaold$id <- lisaold$LINNEID

    ## lisaold <- addPer(lisaold, name = "period", cuts = seq(1986, 2014, by = 2)) ## Later! 
    ## liss <- addPer(liss, name = "period", cuts = seq(2002, 2014, by = 6)) # Later!!
    ##liss <- liss[!is.na(liss$hisclass), ]
    ##liss$hisclass <- cut(liss$hisclass, c(0, 2.5, 4.5, 5.5, 8),
      ##                   labels = 1:4)
    ##liss$hisclass <- as.numeric(as.character(liss$hisclass))
    ##liss <- liss[with(liss, !is.na(civst) &
      ##                      !is.na(hisclass)), ]
    ##lisaold <- lisaold[with(lisaold, !is.na(civst)), ]
    liss$civst <- factor(liss$civst,
                         labels = c("unmarried", "married", "prev.married"))
    lisaold$civst <- factor(lisaold$civst,
                         labels = c("unmarried", "married", "prev.married"))
    liss$urban <- liss$FORSAMLING %in% c(248001, 248002, 284004,
                                         284005, 248011, 248201, 248204)
    lisaold$urban <- lisaold$FORSAMLING %in% c(248001, 248002, 284004,
                                         284005, 248011, 248201, 248204)
    liss$id <- liss$LINNEID
    liss <- liss[, c("id", "AR", "birthdate", "sex", "enter", "exit", "event",
                     "urban", "civst", "hisclass", "ULORSAK")]
    liss$dataset <- paste("lisa", as.character(liss$AR), sep = "")
    save(liss, file = "liss2.rda")
    save(lisaold, file = "lisaold.rda")
```

Now, read *checkData* (maybe not).

>>>>

```{r lisadat}
load("../../Data/lisa.rda")
lisa <- lisa[(lisa$KOMMUN %in% ourkom) & (lisa$LINNEID %in% per$LINNEID), ]
indx <- match(lisa$LINNEID, per$LINNEID)

lisa$birthdate <- per$birthdate[indx]

```

@@

```{r cleanandsort}
##lisadata <- age.window(lisa, c(40, 110))
lisadata <- lisa[order(lisa$LINNEID, lisa$enter), ]
lisadata <- cal.window(lisadata, c(1987, 2014)) # 'Remove lisa2013'
rownames(lisadata) <- 1:NROW(lisadata)
##save(lisadata, file = "lisadata2.rda")
```

@@

@@

    ## Fix HISCLASS:
    source("R/ssyk3TOhisclass.R")
    ##ssyk3TOhisclass
    lisadata$hisclass <- ssyk3TOhisclass(lisadata$SSYK3)
    ## Push forward:
    source("R/pushHis.R")
    ## liss <- pushHis(lisadata) # Later!
    liss <- lisadata
    ##liss$hisclass <- liss$nyhisclass
    ##liss$nyhisclass <- NULL
    ## Now:
    ##liss <- group_by(lisadata, LINNEID) %>% fill_("hisclass") # Later!!
    liss$id <- liss$LINNEID
    ##lisaold$id <- lisaold$LINNEID

    ## lisaold <- addPer(lisaold, name = "period", cuts = seq(1986, 2014, by = 2)) ## Later! 
    ## liss <- addPer(liss, name = "period", cuts = seq(2002, 2014, by = 6)) # Later!!
    ##liss <- liss[!is.na(liss$hisclass), ]
    ##liss$hisclass <- cut(liss$hisclass, c(0, 2.5, 4.5, 5.5, 8),
      ##                   labels = 1:4)
    ##liss$hisclass <- as.numeric(as.character(liss$hisclass))
    ##liss <- liss[with(liss, !is.na(civst) &
      ##                      !is.na(hisclass)), ]
    ##lisaold <- lisaold[with(lisaold, !is.na(civst)), ]
    liss$civst <- factor(liss$civst,
                         labels = c("unmarried", "married", "prev.married"))
    ##lisaold$civst <- factor(lisaold$civst,
      ##                   labels = c("unmarried", "married", "prev.married"))
    liss$urban <- liss$FORSAMLING %in% c(248001, 248002, 284004,
                                         284005, 248011, 248201, 248204)
    ##lisaold$urban <- lisaold$FORSAMLING %in% c(248001, 248002, 284004,
      ##                                   284005, 248011, 248201, 248204)
    liss$id <- liss$LINNEID
    liss <- liss[, c("id", "AR", "birthdate", "sex", "enter", "exit", "event",
                     "urban", "civst", "hisclass", "ULORSAK")]
    ##liss$dataset <- paste("lisa", as.character(liss$AR), sep = "")
    save(liss, file = "liss2.rda")
    ##save(lisaold, file = "lisaold.rda")
```

# Combine Fob and Lisa

```{r combfoblisa}
source("R/fixCovar2.R")
foli <- rbind(fobb, liss)
foli <- foli[order(foli$id, foli$enter), ]
source("R/pushForward.R")
foli$hisclass <- unlist(tapply(foli$hisclass, foli$id, pushForward))
foli$hisclass[is.na(foli$hisclass)] <- 5
foli$hisclass <- factor(foli$hisclass, labels = c("elite", "middle", "worker", "farmer", "none"))
foli$hisclass40 <- fixCovar2(foli$id, foli$hisclass, foli$enter, foli$exit, age = 40, lookBack = 20)
foli$hisclass65 <- fixCovar2(foli$id, foli$hisclass, foli$enter, foli$exit, age = 65, lookBack = 45)
save(foli, file = "foli.rda")
```
